%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%############


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Mohd Tashwaruddin Safin} \\ \vspace{1pt}
    \small 01985511517 $|$ \href{mailto:taswaruddin517@gmail.com}{\underline{taswaruddin517@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/tashwar-uddin-safin-7676b0237/}{\underline{linkedin.com/in/safin}} $|$
    \href{https://github.com/Taswaruddin007}{\underline{github.com/safin}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Brac University}{Merul Badda, Dhaka}
      {Bachelor of Science in Computer Science and Engineering (CGPA: 3.92/4.00)}{Oct. 2021 -- Sep 2026}
      \resumeItemListStart
        \resumeItem{\textbf{Core Coursework:} Data Structures and Algorithms, Database Management Systems, Software Engineering, Operating Systems, Object-Oriented Programming, Computer Networks.}
     \resumeItemListEnd
    \resumeSubheading
      {Birshreshtha Munshi Abdur Rouf Public College}{BGB Head Quarters, Dhaka}
      {Higher Secondary School Certificate in Science (GPA: 5.00/5.00)}{Jul. 2018 -- Apr. 2020}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, Express, Material-UI} \\
     \textbf{Developer Tools}{: Git, GitHub, Google Cloud Platform, Supabase, VS Code, PyCharm, Code-blocks} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Seaborn, PyTorch}
    }}
 \end{itemize}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart          
      \resumeProjectHeading
    {\textbf{NeuraRig} $|$ \emph{MERN Stack (MongoDB, Express, React, Node.js), Groq API, JWT}}{Feb. 2025 -- May. 2025}
    \resumeItemListStart
      \resumeItem{Architected an AI-powered e-commerce platform for computer accessories with full CRUD capabilities for system administrators.}
      \resumeItem{Leveraged the Groq API to build a specialized hardware chatbot capable of parsing user constraints to ensure build compatibility.}
      \resumeItem{Secured client-server communication using stateful cart storage, JWT-driven authentication sessions, and securely encrypted user databases.}
      \resumeItem{Optimized application UX with seamless React Router navigation, detailed product rating workflows, and a full checkout pipeline.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Sphere} $|$ \emph{MERN Stack, Socket.IO, Supabase Storage, Leaflet, Google OAuth}}{Oct. 2025 -- Jan. 2026}
    \resumeItemListStart
      \resumeItem{Developed a multi-tier university community platform featuring real-time chat, learning management systems, and group forums.}
      \resumeItem{Designed and implemented a modular backend API with Express using strict input validation middleware and Mongoose object modeling.}
      \resumeItem{Built automation features including a resume/CV data extractor to seamlessly populate user portfolios and academic histories.}
      \resumeItem{Optimized frontend state and map rendering using React 19, Material-UI (MUI), and Leaflet map component APIs.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Undergraduate Student Tutor}{Feb. 2025 -- Present}
      {Brac University}{Merul Badda, Dhaka}
      \resumeItemListStart
        \resumeItem{Facilitate student learning paths by breaking down complex concepts in foundational CSE courses.}
        \resumeItem{Conduct weekly review sessions and offer guidance on debugging assignments and algorithmic logic.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS & ACHIEVEMENTS-----------
\section{Certifications \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Academic Awards}{: e.g., Received Performance-Based Scholarship at Brac University / Dean's List (Spring 2024)}
    }}
 \end{itemize}


%-----------EXTRACURRICULAR ACTIVITIES-----------
\section{Extracurricular Activities}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Brac University Computer Club (BUCC)} $|$ \emph{Former Member}}{Jan. 2022 -- Mar. 2023}
      \resumeItemListStart
        \resumeItem{Participated in internal hackathons, technical workshops, and assisted in organizing university tech-fests.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}